Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex
adding another table

@@

@@

\textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage.

>>>>

\subsection{TOGGLE\_SPAGHETTI (Combinatorial Toggles)}
\begin{table}[!h]
\caption{TOGGLE\_SPAGHETTI}
\centering
\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
 Description & This smell is observed when the execution of code is controlled by combination of states of several toggles.  \\ \hline

 Example & 
 \begin{lstlisting}
 if(command_line->HasSwitch(
     s::kTestLauncherTotalShards) &&
     command_line->HasSwitch(
         s::kTestLauncherShardIndex)
     ){
 if(!StringToInt(
      command_line
      ->GetSwitchValueASCII(
          s::kTestLauncherTotalShards),
          &total_shards)){
      LOG(ERROR) << "Invalid value for " <<    
      s::kTestLauncherTotalShards;
      return false;
  }
 \end{lstlisting}
 \\ \hline

 Possible reasons for their presence &

 \begin{enumerate}
 \item{Mix of canary use cases or A/B testing in toggle block could result in this kind of spaghetti code.}
 \item{Inconsistency in API’s used to manage toggles and canary use cases.}
 \item{Presence of more than one API to manage feature flags. Transition from legacy feature toggles to more formal one.}
 \end{enumerate}
 \\ \hline

 Consequences & If this smell is observed it will have the following consequences in the project
Cost of testing will increase so as to cover all the code paths.
Changing existing code base will become non-trivial.
Code complexity is higher, difficult to understand.
 \\ \hline

@@

\begin{figure*}
\includegraphics[height=6in,width=7in]{figure/uml.png}
\caption{UML Class Diagram.}
\label{fig:uml}
\end{figure*}

@@

\textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage. Figure~\ref{fig:uml} represents the design of our 
approach in an UML diagram.
